Enabling the Use of GPU Virtualization in Cloud Environments

### 2015-10-21 paper.tex
primera version introduccion

\section{\uppercase{Introduction}}
\label{sec:introduction}

>>>>

\section{\uppercase{Introduction}}
\label{sec:introduction}
The use of coprocessor and accelerators has been continuously
growing in the past several years and 90 supercomputers
were equipped with accelerators of some sort in the most 
recent TOP500 list~\cite{nov14top500}, dated June 2015.  
These devices achieve better performance than traditional processors for
codes which match their architecture.

These devices were general adopted with the release of the CUDA programming model for
NVIDIA GPUs~\cite{cuda65}. This libraries include both high- and low-level application programming interfaces (APIs)
to allow the use of NVIDIA devices as general-purpose
accelerators.  
Following CUDA, OpenCL~\cite{opencl} appeared as an attempt
to offer a cross-vendor solution.

The current approach for creating clusters with GPUs has been to
install one or more of these devices in each compute node. 
However, these configurations present a low
utilization rate of the computational resources  
 because of mismatches between the application's type of parallelism
and the accelerators' architecture.

In order to address this problem, remote virtualization was proposed 
and several solutions have been presented (e.g. {rCUDA}~\cite{tonithesis,toniparco},
DS-CUDA~\cite{dscuda}, gVirtus~\cite{gvirtus}, vCUDA~\cite{vcuda}, VOCL~\cite{vocl}, and SnuCL~\cite{snucl}).

Among the virtualization frameworks, the most
prominent is {rCUDA}, which
enables cluster configurations with fewer GPUs than nodes.  With this
approach, GPU-equipped nodes act as GPGPU (general-purpose GPU), enabling a CUDA-sharing solution that potentially achieves 
 a higher overall GPU load in the system.
